|

### 2024-11-01 manuscript/paper.Rmd
manuscript edits

## Modeling fossil stickleback trait means through time for males and females
 The goal of our analysis was to estimate fossil trait means through time, by sex, while incorporating uncertainty across imputations in the classification of sex. As we explain in this section, we are implementing a complex model structure to account for the fact that the rate of change in the mean of the trait over time may be a non-constant value. In addition, we are using multiple imputation procedure to account for the fact that the sex is unobserved in the fossils in addition to other pieces of information that are missing. We implement a Bayesian approach because these methods are more effective for analyzing hierarchical model structures as well as incorporating missing data.<!--We used a Bayesian approach to estimate trait means in part because imputation is the process of sampling from a posterior predictive distribution of missing data, given observed data. \textcolor{red}{Matt, THIS NEEDS MORE WORK TO JUSTIFY THE BAYESIAN APPROACH, EXPLAINING IT TO MY AUDIENCE. -YS}  -->

@@

Continuous traits will likely have some correlation with standard length (i.e., allometry) (@Huxley1932)(@Vojeetal2022)(@Vojeetal2014). We account for this by adding an additional parameter, $\gamma_k$. In addition, the continuous traits ds1, ds2, ds3, lps, tpg are unique in that these traits tend to be lost over time, results in a proportion of zeros in our empirical dataset. For these random variables, we add binary variable $Z_{ij}$, where $Z_{k,ij} = 1$ means that the trait is lost, and $Z_{k,ij} = 0$ means the trait is observed. For all other continuous traits, we assume $Z_{k,ij} = 0$ <!--We also define $Y_{k,ij}$ as -->

>>>>

## Modeling fossil stickleback trait means through time for males and females
 The goal of our analysis was to estimate fossil trait means through time, by sex, while incorporating uncertainty across imputations in the classification of sex. As we explain in this section, we are implementing a complex model structure to account for the fact that the rate of change in the mean of the trait over time may be a non-constant value. We implement a Bayesian approach because these methods are more effective for analyzing the hierarchical model structures we implement. <!--We used a Bayesian approach to estimate trait means in part because imputation is the process of sampling from a posterior predictive distribution of missing data, given observed data. \textcolor{red}{Matt, THIS NEEDS MORE WORK TO JUSTIFY THE BAYESIAN APPROACH, EXPLAINING IT TO MY AUDIENCE. -YS}  -->

@@

Continuous traits will likely have some correlation with standard length (i.e., allometry) (@Huxley1932)(@Vojeetal2022)(@Vojeetal2014). We account for this by adding an additional parameter, $\gamma_k$. In addition, the continuous traits ds1, ds2, ds3, lps, tpg are notable because they tend to be lost during the evolution of armor reduction in this system (CITATIONS). This generates meaningful zeros for trait lengths in our empirical dataset that \textcolor{red}{MATT, help describing why we wanted to analyze with and without 0s? -YS}. For these random variables, we added the binary variable $Z_{ij}$, where $Z_{k,ij} = 1$ means that the trait is lost, and $Z_{k,ij} = 0$ means the trait is observed. For all other continuous traits, we assume $Z_{k,ij} = 0$ <!--We also define $Y_{k,ij}$ as -->
